# Data preparation and cleaning {#datachecks}   

## Raw dataset {#rawdata}

**included studies**   
```{r setup, include=FALSE, echo = FALSE, warning = FALSE, message = FALSE}
#--- setup ---------------------------------------------------------------------
# load data
library(readxl)
library(tidyverse)
library(knitr)
library(kableExtra)
library(foreign)
library(ggplot2)
library(ggExtra)
library(RColorBrewer)
library(kableExtra)
library(papaja)

# source('MA_cross_dataPrep.R')
load('MA_data_cross.RData')
```


Our thorough literature review identified potentially relevant studies based on predefined keywords.       
After screening of eligible studies, the _raw_ data set includes:   
  - `r length(unique(data$Paper))` manuscripts  
  - `r length(unique(data$Study))` studies  
  - `r length(unique(data$SS))` independent samples of participants  


_# effect sizes per paper_  
```{r es_counts, echo = FALSE}
# combine included + excluded 
study_data <- rbind(data, data_excluded) %>%
  dplyr::select(Paper, SS, SubSample, Study, nExp, nCtl, males_AVGP, males_NVGP, MaleRatioDiff) %>%
  unique() 

# check number of ES per subject sample
study_data %>%
  # remove Dale and Green 2017 Overt-  & Covert- only samples, we included combined sample
  filter(!grepl(x = SubSample, pattern = "overt only")) %>%
  # remove Male-Only samples (obtained after)   
  filter(SubSample != "male only") %>%
  group_by(Paper) %>%
  summarise(es = n()) %>%
  summarise(
    manuscripts = n(), 
    effects = sum(es),
    es_min = min(es),
    es_max = max(es),
    es_median = median(es),
    es_Q1 = quantile(es, .25),
    es_Q3 = quantile(es, .75)
  ) %>%
  kable() %>%
  kable_paper(html_font = "helvetica", lightable_options = c("stripped", "hover"), full_width = FALSE, position = "left")
```


Second, we checked gender distributions of the AVGP and NVGP groups.

```{r genderDistrib, echo = FALSE}
mycols <- brewer.pal(name = "RdYlGn", n = 6)
a <- study_data %>%
  # remove Dale and Green 2017 Overt-  & Covert- only samples, we included combined sample
  filter(!grepl(x = SubSample, pattern = "overt only")) %>%
  # remove Male-Only samples (obtained after)   
  filter(SubSample != "male only") %>%
  ggplot(., aes(x = males_AVGP, y = males_NVGP, 
                            fill = MaleRatioDiff, 
                            col = (abs(MaleRatioDiff)<.2)))+
  geom_point(alpha=.8, cex = 3, shape = 21) +
  geom_smooth(method = "glm", col = "steelblue", fullrange = TRUE)  +
  geom_abline(intercept = .2, slope = 1, lty = 2, col = "darkgreen", size = .6) +
  geom_abline(intercept = -.2, slope = 1, lty = 2, col = "darkorange", size = .6) +
  scale_color_manual(values = c("tomato","limegreen")) +
  scale_fill_distiller(type = "seq", palette = "RdYlGn", limits = c(-1, 1), n.breaks = 6) +
  labs(fill = "AVGP - NVGP difference\n") +
  guides(col = "none") +
  theme_apa() +
  xlim(0, 1) + 
  ylim(0, 1) +
  coord_fixed(ratio = .8)+
  theme(legend.position = "bottom", legend.box = "black")

ggExtra::ggMarginal(a, type = "histogram", 
                         xparams = list(binwidth = .05, fill = "steelblue", size = .01),
                         yparams = list(binwidth = .05, fill = "steelblue", size = .01))
```
  
There is a predominance of males in both AVGPs and NVGPs. 
The green and orange dashed lines define 3 regions on the between-group difference 
in the proportion of males:   
  - The upper left region (above green) contains studies with greater proportion of males in NVGPs  
  - The bottom right corner (below orange) contains studies with more males in AVGPs    
  - Between these two lines are studies with less than 25% difference in gender ratio  
  

There is a bias toward having more males in the AVGP group.  
Therefore, only studies with a difference in gender ratio less than 25% 
will be included in subsequent plots and analyses


These studies are shown with a green contour   

```{r genderPlot, echo = FALSE}
study_data %>%
  # remove Dale and Green 2017 Overt-  & Covert- only samples, we included combined sample
  filter(!grepl(x = SubSample, pattern = "overt only")) %>%
  # remove Male-Only samples (obtained after)   
  filter(SubSample != "male only") %>%
  ggplot(., aes(x = MaleRatioDiff, fill = MaleRatioDiff, 
                            group = MaleRatioDiff,
                            col = (abs(MaleRatioDiff)<.2))) +
  geom_histogram(binwidth = .05) + 
  geom_vline(xintercept = -.2, lty = 2, col = "darkgreen", size = .6) +
  geom_vline(xintercept = .2, lty = 2, col = "darkorange", size = .6) +
  scale_color_manual(values = c("tomato","limegreen")) +
  scale_fill_gradient2(low = "white", mid = "gray", high = "black", midpoint = 0, limits = c(-1, 1)) +
  scale_fill_distiller(type = "seq", palette = "RdYlGn", limits = c(-1, 1)) +
  labs(x = "male ratio difference") +
  xlim(-1, 1) +
  guides(fill = "none", col = "none") +
  theme_apa()
```

When the difference exceeded 20%, authors were contacted in order to obtain data 
from male-only samples, only if a minimum of 10 participants in each group.   


**excluded studies**   

Studies excluded at the data extraction stage for various reasons: gender imbalance, criteria  for defining AVGP or NVGPs, etc.   
_# effect sizes per paper - excluded studies only_   
```{r echo = FALSE}
# keep only male-only data
data_excluded %>%
  dplyr::select(Paper, SS, SS_overlap, SubSample, Study, nExp, nCtl, males_AVGP, males_NVGP, MaleRatioDiff) %>%
  unique() %>% 
  # filter(SubSample != "male only") # exclude male-only samples and take only original full sample
  group_by(Paper) %>%
  summarise(es = n()) %>%
  summarise(
    studies = n(),
    effects = sum(es)) %>%
  kable() %>%
  kable_paper(html_font = "helvetica", lightable_options = c("stripped", "hover"), full_width = FALSE, position = "left")


#--- STUDIES EXCLUDED BECAUSE OF GENDER IMBALANCE ------------------------------
excluded_Papers <- unique(data_excluded$Paper)
included_Papers <- unique(data$Paper)
Papers_tocheck_gender <- c(excluded_Papers[excluded_Papers %in% included_Papers],
                           included_Papers[included_Papers %in% excluded_Papers])

data_tocheck <- rbind(data %>% filter(Paper %in% Papers_tocheck_gender),
                      data_excluded %>% filter(Paper %in% Papers_tocheck_gender)) %>%
  dplyr::select(Paper, SS, SS_overlap, SubSample, Study, 
                nExp, nCtl, males_AVGP, males_NVGP, MaleRatioDiff, 
                Cognitive_domain, Task, Measure, g, g_var) %>%
  arrange(Paper, SS, Cognitive_domain, Task, Measure)
# write_csv(data_tocheck, file = "/Users/bediou/GoogleDrive/Meta-Analysis/DATA/ANALYSIS/2021/MA_cross_tocheck.csv")
```


## Filtered dataset (i.e., matched gender)  {#cleandata}  

Effect sizes as well subject and study characteristics were then extracted from all studies that were eligible.   

```{r recoding, echo = FALSE}
# define moderators to recode as factor
moderators <- c("Cognitive_domain", "DV_type", "Effect", "Recruitment")
domains <- c("perception", 
             "motor control", 
             "bottom-up attention", 
             "top-down attention", 
             "inhibition", 
             "spatial cognition", 
             "multi-tasking", 
             "verbal cognition", 
             "problem solving")

es_data <- data %>% 
  filter(!is.na(keep), keep != "IQ") %>% 
  mutate_at(vars(Paper:SS_overlap), factor) %>%# recode cluster info as factor
  mutate_at(vars(moderators), factor) %>%# moderators as factor
  mutate(Cognitive_domain = factor(Cognitive_domain, 
                        levels = domains, 
                        ordered = FALSE)) %>%
  mutate(Paper = as.character(Paper)) %>%# recode paper as character (or wald_test _0.53 crashes)
  mutate(g_se = sqrt(g_var),# add significance
         z = g / sqrt(g_var),
         p.2t = 2*pnorm(z, lower.tail = F),
         p.1t = pnorm(z, lower.tail = F)) %>%
  mutate(pSignif.2t = if_else(p.2t < .05, "significant", "non-significant")) %>%
  # Create new variable for Egger Sandwich/Egger MLMA analysis as well as ES ID variable for MLMA
  mutate(Va = 4 / (nExp + nCtl), 
         sda = sqrt(Va),
         ES_ID = factor(1:nrow(.))) #%>%
  # filter(!is.na(g)) # There are missing values for g so I dropped them to test the code fully. 
```


After exclusion of studies with unbalanced gender, the final data set includes:  
  - `r nrow(es_data)` effect sizes   
  - `r length(unique(es_data$Paper))` papers   
  - `r length(unique(es_data$Study))` studies   
  - `r length(unique(es_data$SS))` independent samples     
  
```{r EScounts_clean, echo = FALSE}
es_data %>%
  group_by(Paper) %>%
  summarise(es = n()) %>%
  summarise(
    manuscripts = n(), 
    effects = sum(es),
    es_min = min(es),
    es_max = max(es),
    es_median = median(es),
    es_Q1 = quantile(es, .25),
    es_q3 = quantile(es, .75)
  ) %>%
  kable() %>%
  kable_paper(html_font = "helvetica", lightable_options = c("stripped", "hover"), full_width = FALSE, position = "left")
``` 


The figure Below shows the number of effect sizes extracted from each manuscript, study or subject sample...   
```{r EShistograms, echo = FALSE}
par(mfrow = c(3,1))
hist(table(es_data$Study), main = "# ES per Study", xlab = "# ES", breaks = seq_len(20)) 
hist(table(es_data$Paper), main = "# ES per Paper", xlab = "# ES", seq(0,20,1)) 
hist(table(es_data$SS), main = "# ES per Subject Sample", xlab = "# ES", breaks = seq(0, 20, 1)) 
```


Most studies contributed only few effects.  

---------------

Notes:   
- Studies are embedded in Papers.  
- There are cases of overlap in participants across studies and papers   
  o Studies reported in a paper can involve overlapping samples of participants   
  o Samples of participants (complete or partial) can be reported in several studies or papers     

---------------



## Moderators
```{r esDistrib, echo = FALSE}
# print(dfSummary(es_data, graph.magnif = 0.75, valid.col = FALSE), 
#       max.tbl.height = 600, method = "render")

# DataExplorer::create_report(es_data, output_file = "EffectSizes_DataExplorer_output.html")
es_data %>% 
  mutate("Cognitive_domain " = as.character(Cognitive_domain)) %>%
  pivot_longer(cols = c("Cognitive_domain ", "DV_type", "Effect", "Recruitment"), 
                         names_to = "Moderator", values_to = "Level") %>%
  group_by(Moderator, Level) %>%
  dplyr::summarise(n = n()) %>%
  # ggplot(.,aes(x = Level, y = n, fill = Moderator))+
  # geom_bar(stat = "identity")+
  # # coord_flip()+
  # facet_grid(~Moderator, drop = TRUE, scales = "free_x")+
  # theme_apa()
  kable() %>%
  kable_styling(bootstrap_options = c("condensed", "striped", "hover"), full_width = FALSE, position = "left") %>%
  collapse_rows(columns = 1, valign = "top")
```

> _note: problematic levels will be recoded before moderator analysis_     


### Number of effect sizes and studies (i.e. manuscript) in each cognitive domain    
```{r nESbyCogDom}
es_data %>% 
  group_by(Cognitive_domain, ) %>%
  dplyr::summarise(n_es = n(), n_studies = length(unique(Study)), n_papers = length(unique(Paper))) %>%
  ggplot(., aes(x = reorder(Cognitive_domain, n_es), y = n_es, fill = Cognitive_domain))+
  geom_bar(stat = "identity")+
  geom_text(colour="white", size=3.5,
           aes(label=paste(n_papers, n_es, sep="/"), y=0.5*n_es))+
  coord_flip()+
  labs(x = "")+
  ggsci::scale_fill_jco()+
  guides(fill = "none")+
  theme_apa()+
  labs(title= "number of effect sizes / papers per cognitive domain")
```


### List of Tasks and Cognitive Domains   

<details>
  <summary>Click to expand!</summary>
```{r CogDomTasks, echo = FALSE}
es_data %>% 
    group_by(Cognitive_domain, Task, Measure) %>%
  # dplyr::summarise(n_es = n()) %>%
  # arrange(Cognitive_domain, Task, Measure) %>%
  dplyr::summarise(examples = unique(Task)) %>%
  group_by(Cognitive_domain, examples) %>%
  summarise(measures = unique(Measure)) %>%
  arrange(Cognitive_domain, examples, measures) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed", "striped", "hover"), full_width = FALSE, position = "left") %>%
  collapse_rows(columns = 1, valign = "top")
```
</details>  



