# TO DO's / exploratory analyses  {#todos}

```{r }
library(tidyverse)
library(kableExtra)
library(DT)
```


## Including studies with unmatched gender groups?   
I could focus on studies for which we obtained gender-matched data and compare with the
original data reported in the paper with unmatched genders?   
However, because I contacted authors to ask for male-only data, I'd need to check 
how much data I am missing data to compute the original (gender unmatched) effects... 


## Subgroup analyses 
Adding with moderators and precision estimate to find the source of heterogeneity (and small-study effect).      


## Moderator Joint Publication Group   
Not sure how to do the clustering...  
We could parse the text and focus on surnames?     
```{r }
unique(es_data$Authors) %>% as.data.frame() %>% datatable()
```


**Cognitive sub-domains**    
The following spatial and verbal tasks with a working-memory component will be re-coded 
as measuring working memory instead of measuring spatial vs verbal skills.    
```{r }
es_data %>% 
  filter(SubDomain != Cognitive_domain) %>%
  group_by(Cognitive_domain, SubDomain) %>%
  dplyr::summarise(examples = unique(Task)) %>%
  arrange(Cognitive_domain, SubDomain, examples) %>%
  kable() %>%
  kable_paper(html_font = "helvetica", lightable_options = c("stripped", "hover"), full_width = FALSE, position = "left") %>%
  collapse_rows(columns = 1:2, valign = "top")
```

Please, check Table _List of Tasks and Cognitive Domains_ to see if tasks may be missing.    


## Analysis on full dataset (i.e., without excluding studies based on gender ratio)   
We excluded quite a large number of studies based on gender ratio.  
Follow-up analyses will examine whether those studies that were excluded appear to have 
a different ES distribution than those we kept.  And I always think it's nice to anticipate 
possible bad faith complaints (i.e., we excluded those studies on theoretical grounds, 
because those types of gender ratios make it impossible to separate gender effects from gaming effects; 
but it's nice to be able to say that if we had kept them, it wouldn't have made a difference empirically).  



## Task difficulty   
USE mean performance (%error, % correct, RT) as a measure of task difficulty to check impact on ES's? 
